Information Distribution Depends on a Language's Grammar and Sounds

### 2019-01-29 cogsci/position-info.Rmd
incorporating switchboard code

---
title: "Information is Not Communicated Uniformly: Evidence from Spoken and Written Corpora"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

These theories model the process of communication as transmission of information over a noisy channel. The producer begins with an intended meaning, packages this meaning into a linguistic format, and then sends it to the receiver over a communcative channel. The receiver must then decode from the signal they receive on their end of the chanel the producer's intended meaning. The problem is that the channel is noisy, and sometimes the signal can get corrupted (e.g. the producer can misspeak, or the receiver can mishear). In order to maximize the probability that the correct meaning is transmitted, these theories predict that producers should choose linguistic messages that keep the rate of information across words constant. The intuition is that if the receiver misperceives a word, and that word contains most of the information in the sentence, then the communication will have failed. Because producers cannot predict which word a speaker will mishear, their best strategy is spread the information evenly across all of the words in a sentence, i.e. maintain *uniform information density* [@genzel2002; @levy2007].

@@

Recently, @yu2016 developed a more direct test of the Uniform Information Density hypothesis, applying the logic used by @genzel2002 to look at the distribution of information *within* individual sentences. <!-- **SOME HIGHER LEVEL DESCRIPTION HERE, WE'll GET INTO THE DETAILS BELOW** -->Because people process language incrementally--using the previous words in a sentence to predict the words that will come next, the amount of information that a word contains when seen in isolation should increase over the course of a sentence. Analyzing a large corpus of written English, they find a different pattern: Entropy increases over the first few words of an utterance and then remains constant until the final word where it again jumps up (see Figure \ref{fig:our_replication}). @yu2016 conclude that the Uniform Information Density hypothesis must not hold for medial words in a sentence.

We extend and generalize @yu2016 in three ways: we confirm that this same pattern is found in spoken English--in both adult and child speakers. We then examine entropy curves cross-linguistically, finding a diversity of shapes across the world's languages. Finally, we show that entropy curves are predictable from the structure of individual languages, namely word order. Taken together, our results suggest a refinement of the Uniform Information Density hypothesis: Speakers may choose to order words in order to preserve uniform information, but they must do so under prior constraints on word order imposed by the language they speak.

@@

Switchboard [To be put in]

We used the Providence English corpds from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

@@

[Put in an illustration of the slope sections and treatments here?]

@@

# Conclusions 
In this paper, we have characterized and applied a model based on Genzel & Charniak (2002) for distinguishing entropy at each word position within sentences. In doing so, we have provided evidence against the Uniform Information Density hypothesis. Our work indicates that information is not distributed uniformly throughout an utterance regardless of languages, but that languages possess a characteristic information distribution determined by their syntactic, morphological and phonological features.

>>>>

---
title: "Information Distribution Depends on a Language's Grammar and Sounds"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

These theories model the process of communication as transmission of information over a noisy channel. The producer begins with an intended meaning, packages this meaning into language, and then sends the meaning to their intended receiver over a communcative channel. The receiver must then decode from the signal they receive on their end of the channel the producer's intended meaning. The problem is that the channel is noisy, and sometimes the signal can get corrupted (e.g. the producer can misspeak, or the receiver can mishear). In order to maximize the probability that the correct meaning is transmitted, these theories predict that producers should choose linguistic messages that keep the rate of information across words constant. The intuition is that if the receiver misperceives a word, and that word contains most of the information in the sentence, then the communication will have failed. Because producers cannot predict which word a speaker will mishear, their best strategy is spread the information evenly across all of the words in a sentence, i.e. maintain *uniform information density* [@genzel2002; @levy2007].

@@

Recently, @yu2016 developed a more direct test of the Uniform Information Density hypothesis, applying the logic used by @genzel2002 to look at the distribution of information *within* individual sentences. <!-- **SOME HIGHER LEVEL DESCRIPTION HERE, WE'll GET INTO THE DETAILS BELOW** -->Because people process language incrementally--using the previous words in a sentence to predict the words that will come next--the amount of information that a word contains when seen in isolation should increase over the course of a sentence. Analyzing a large corpus of written English, they find a different pattern: Entropy increases over the first few words of an utterance and then remains constant until the final word where it again jumps up (see Figure \ref{fig:our_replication}). @yu2016 conclude that the Uniform Information Density hypothesis must not hold for medial words in a sentence.

We extend and generalize @yu2016 in three ways: we confirm that this same pattern is found in spoken English--in both adult and child speakers. We then examine entropy curves cross-linguistically, finding a diversity of shapes across the world's languages. Finally, we show that entropy curves are predictable from the structure of individual languages, namely word order. Taken together, our results suggest a refinement of the Uniform Information Density hypothesis: speakers may structure their utterances to optimize information density, but they must do so under the constraints of the language they use to communicate.

@@

```{r switchboard, include=FALSE}

process_switchboard <- function() {

}

unigram_entropy <- function(tokens) {

  tokens %>%
    group_by(word_order, word) %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

tokens <- process_switchboard()

entropies <- map(2:10, ~unigram_entropy("", .x, brown_utterances)) %>%
  bind_rows()

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)
```

We used the Providence English corpus from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

@@

@@

# Discussion 
In this paper, we have characterized and applied a model based on Genzel & Charniak (2002) for distinguishing entropy at each word position within sentences. In doing so, we have provided evidence against the Uniform Information Density hypothesis. Our work indicates that information is not distributed uniformly throughout an utterance regardless of languages, but that languages possess a characteristic information distribution determined by their syntactic, morphological and phonological features.
